### 2018-10-10 doc/plos/text/manuscript.tex
concluding remarks

>>>>

Here we took an approach to nowcasting flu in quasi-real-time using a method
based on the Kalman filter. We used this method to assimilate digital
surveillance and flu forecasts from eight sources spanning 75 distinct
locations within the US.

We showed that accuracy of nowcasts almost always outperforms straightforward
baselines. The advantage of these nowcasts is their extremely low
latency---they are available up to one week before initial wILI publication.

The primary challenge in incorporating additional data sources is accurately
estimating sensor noise covariance. The number of weekly observations required
to estimate covariance at the same resolution grows with the square of the
number of input sensors. To address this problem, a direction for future work
is that of sensor selection---perhaps via LASSO.

Another area of future research is to nowcast additional outbreaks in
additional locations. This, however, depends critically on the availability of
both a rich history of ground truth and an ongoing set of digital surveillance
sources.

Finally, in addition to retrospective nowcasts examined here, ongoing nowcasts
are produced each week and made publicly available both through our website and
our developer API (TODO: citations).
